\documentclass[margin]{res}

\usepackage{fontspec,xltxtra,xunicode}
\usepackage{latexsym}
%\usepackage{xeCJK}

%\defaultfontfeatures{Mapping=tex-text}
%\setCJKmainfont[BoldFont=SimHei,ItalicFont=KaiTi]{SimSun}
\setmainfont{Palatino Linotype}

\textwidth=5.2in % increase textwidth to get smaller right margin

\usepackage[hidelinks]{hyperref}
\begin{document} 

\address{ Qichao Zhang \\ }
\address{ Nanjing University Software Institute, 2010,  Bachelor\\ (+86) 152-9838-8316  \\ \href{http://lecoding.com}{http://lecoding.com} \\ 
\href{mailto:njuzhangqichao@gmail.com}{njuzhangqichao@gmail.com} }

 
\begin{resume} 
 
\section{Technical Skills} 
   \begin{tabular}{l p{3in}}
      \underline{Operating Systems} &  Ubuntu, ArchLinux, Gentoo, CentOS \\
      \underline{Languages} &  C, Java, PHP, JavaScript, C++, Python, Bash \\
      \underline{Softwares} & Vim, Git, GDB, IntelliJ, Eclipse, Maven \\
      \underline{Frameworks} & jQuery, Yii, Backbone, Spring, Spring MVC
 \end{tabular}

\section{Experience} 
{\bf Jiangsu Zhongzheng InfoTech Ltd} \hfill 2012-7-20 to 2012-12-20 
\begin{itemize} \itemsep -2pt 
\item A entrepreneurial team, working on a platform website to serve NJU students, using PHP and Yii Framework.
\item My job here mainly includes: designing the authentication for OAuth2.0 and supplying APIs for the open platform, besides some front-end development (using jQuery and Bootstrap).
\item Here, I learned a lot about team cooperation and font-end to backend interaction.
\end{itemize}

\section{Projects}
{\bf UWS,} A lightweight http web server\hfill 2012 - 2013
\begin{itemize} \itemsep -2pt
  \item Independent Project, developing with C language, aiming to build a high performance http server, it has similar configuration file with {\it nginx}.
  \item Implemented functions: custom error pages, 304 status , deflate and gzip compression, http basic authentication, url rewrite, simple reverse proxy and FastCGI support.
  \item Performance: under Ubuntu in a VMware instance having 512M memory, it can handle 7kqps of {\it apache benchmark} test in single process mode.
  \item To solve the memory leak problem, I wrote a memory pool named {\it usmem}, referring the design of Loki.
  \item I also write a demo site: \href{http://demo.lecoding.com}{http://demo.lecoding.com}
\end{itemize}



{\bf DistMEM,} A NoSQL database\hfill  2012 - 2013
\begin{itemize} \itemsep -2pt
  \item Independent Project, developing with C++. It provides simple APIs, like set,get and del.
  \item It provides simple APIs, like set, get and del. It has 4 data types: int, float, string and list, and string is binary safe.
  \item The data file implementation take the design of the FAT12 file system and it uses B-Tree as index structure, also I add LRU cache for better performance. 
  \item The protocol of communicating refers the {\it Redis} specification, so it's cross-platformed, and I wrote a client console using Python.
  \item Besides, I developed a PHP extension named {\it php\_distmem}(written in C) to supply access to distmem.
\end{itemize}

{\bf NJU Wenji,} A web site for literature lovers \hfill 2012
\begin{itemize} \itemsep -2pt
  \item Cooperative project, based on Yii Framework. It's a project I written with seniors, providing a site for NJU literature lovers. My job mainly includes:
  \item Integrating with SNS and share with others using OAuth2.0
  \item Comment, includes post comments and display
  \item A Markdown-like language interpreter, translating specific article format to HTML
  \item A jQuery plugin of building a dropdown list in a textarea
  \item Other trivial jobs like supplying RESTful APIs and building front-end interaction
\end{itemize}

{\bf UPLEX,} Python Lex interpreter\hfill 2012
\begin{itemize} \itemsep -2pt
  \item Independent project, A lex implementation using Python language, according to <{\it Compilers}>.
  \item Regular expression engine is its core function, using the procedure NFA->DFA->mDFA, we can get a minimized DFA, it can deal with simple regexp. This program can read a *.l file and generate a runnable py file.
\end{itemize}

{\bf Lily-PHP-SDK,} NJU Lily BBS API Wrapper\hfill 2011 - 2012
\begin{itemize} \itemsep -2pt
  \item Independent project, develop with PHP. Lily BBS is too old to supply standard API, so I using curl to craw the site and resolve useable APIs. Here are some sub-projects:
  \item {\it Lily-ME}: A mobile site of Lily BBS using jQuery Mobile and Lily-PHP-SDK.
  \item {\it Lily-Mobile}: This is an android app for Lily BBS, enhanced the bbs and using proxy to save network cost.
\end{itemize}

{\bf Other projects}\hfill 2011 - 2013
\begin{itemize} \itemsep -2pt
  \item Light blog, A blog app based on Yii Framework and jQuery
  \item Remote whiteboard, based on Java and Swing, I am in charge of software architecture, audio transmission and message queue.
  \item Some Python websites on {\it Google App Engine}, like blog, disk and notepad. view online
  \item NJU-Courses-Select chrome plugin, using for grabbing hot courses.
\end{itemize}

\section{Education} 
\begin{tabular}{l p{3in}}
  GPA &  4.1/5.0 \\
  CET4 / CET6 & 617 / 546
\end{tabular}

\section{Links}
\begin{tabular}{l p{3in}}
  \underline{Blog:} & \href{http://lecoding.com}{http://lecoding.com}\\
  \underline{GitHub:} &  \href{https://github.com/usbuild}{https://github.com/usbuild}\\
  \underline{Twitter:} & \href{https://twitter.com/usbuild}{https://twitter.com/usbuild}
\end{tabular}

\end{resume} 
\end{document} 



